Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2015-10-31 paper.tex
Text wrapping

% Abstract (Less than 200 words)
\abstract{The performance and wake characteristics of cross-flow (vertical axis)
    turbines depend on many parameters: solidity, blade profile, blade pitch, number
    of blades, strut drag, operational parameters such as tip speed ratio---and
    Reynolds number. Experiments were performed with a large laboratory-scale high
    solidity cross-flow turbine to investigate Reynolds number effects on
    performance and wake transport characteristics. A key question was what an
    acceptable Reynolds number mismatch is for scaled physical model tests of
    cross-flow turbines, both from the perspective of predicting full scale
    performance and flow dynamics, as well as numerical model validation. It was
    demonstrated that the performance of the cross-flow turbine becomes essentially
    $Re$-independent at a Reynolds number based on turbine diameter of $Re_D \approx
    10^6$, or an approximate Reynolds number based on blade chord of $Re_c \approx 2
    \times 10^5$. A simple model that calculates peak torque coefficient from static
    foil data and cross-flow turbine kinematics was shown to be a reasonable
    estimator for predicting Reynolds number dependence of an actual cross-flow
    turbine operating under dynamic conditions.}

>>>>

% Abstract (Less than 200 words)
\abstract{The performance and wake characteristics of cross-flow (often
    vertical-axis) turbines depend on many parameters: solidity, blade profile,
    blade pitch, number of blades, strut drag, operational parameters such as tip
    speed ratio---and Reynolds number. Experiments were performed with a large
    laboratory-scale high solidity cross-flow turbine to investigate Reynolds number
    effects on performance and wake transport characteristics. A key question was
    what an acceptable Reynolds number mismatch is for scaled physical model tests
    of cross-flow turbines, both from the perspective of predicting full scale
    performance and flow dynamics, as well as numerical model validation. It was
    demonstrated that the performance of the cross-flow turbine becomes essentially
    $Re$-independent at a Reynolds number based on turbine diameter of $Re_D \approx
    10^6$, or an approximate Reynolds number based on blade chord of $Re_c \approx 2
    \times 10^5$. A simple model that calculates peak torque coefficient from static
    foil data and cross-flow turbine kinematics was shown to be a reasonable
    estimator for predicting Reynolds number dependence of an actual cross-flow
    turbine operating under dynamic conditions.}
